Using Graphical Models for Novelty Detection on Semantic Room Classification

### 2011-05-12 semantic-nd/article.tex
Code to run experiments for paper added.

\begin{figure}[h!]
\centering
\includegraphics[width=0.40\textwidth]{figures/roc-simple.pdf}

This graph is from a previous experience. Where there was even no need for the normalizing factor.

@@

\subfloat[3 sensed variables]{\includegraphics[width=0.40\textwidth]{figures/roc-simple.pdf}}
\qquad
\subfloat[5 sensed variables]{\includegraphics[width=0.40\textwidth]{figures/roc-simple.pdf}}

\subfloat[10 sensed variables]{\includegraphics[width=0.40\textwidth]{figures/roc-simple.pdf}}
\qquad
\subfloat[50 sensed variables]{\includegraphics[width=0.40\textwidth]{figures/roc-simple.pdf}}

>>>>

\begin{figure}[h!]
\centering
\includegraphics[width=0.60\textwidth]{results/synthetic-all.pdf}

@@

\subfloat[3 sensed variables]{\includegraphics[width=0.40\textwidth]{results/synthetic-3features.pdf}}
\qquad
\subfloat[5 sensed variables]{\includegraphics[width=0.40\textwidth]{results/synthetic-5features.pdf}}

\subfloat[10 sensed variables]{\includegraphics[width=0.40\textwidth]{results/synthetic-10features.pdf}}
\qquad
\subfloat[50 sensed variables]{\includegraphics[width=0.40\textwidth]{results/synthetic-50features.pdf}}
